### 2018-01-30 README.Rmd
fix funding notices

<!--
Note about shrinkage of influence curves, adapting @smyth2004linear.
More exposition here....
-->

@@

<!--
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
-->

@@

        @article{hejazi2017methyvim,
          doi = {},
          url = {},
          year  = {2017},
          month = {},
          publisher = {},
          volume = {},
          author = {Hejazi, Nima S and Hubbard, Alan E and {van der Laan}, Mark
            J},
          title = {methyvim: Targeted and model-free differential methylation
            analysis in R},
          journal = {}
        }

@@

The development of this software was supported in part through a grant from the
National Library of Medicine of the NIH (T32 LM012417).

@@

&copy; 2017 [Nima S. Hejazi](http://nimahejazi.org)

>>>>

@@

## Example

For details on how to best use `methyvim` to perform data-adaptive estimation
and obtain nonparametric inference in the context of differential methylation
analyses, please consult the most recent [package vignette](http://bioconductor.org/packages/release/bioc/vignettes/methyvim/inst/doc/using_methyvim.html)
available through the [Bioconductor
project](https://bioconductor.org/packages/methvim).

@@

        @article{hejazi2018methyvim,
          doi = {},
          url = {},
          year  = {2018},
          month = {},
          publisher = {},
          volume = {},
          author = {Hejazi, Nima S and Phillips, Rachael V and Hubbard, Alan E
            and {van der Laan}, Mark J},
          title = {methyvim: Targeted and model-free differential methylation
            analysis in R},
          journal = {}
        }

@@

The development of this software was supported in part through grants from the
National Institutes of Health: [T32 LM012417-02](https://projectreporter.nih.gov/project_info_description.cfm?aid=9248418&icde=37849831&ddparam=&ddvalue=&ddsub=&cr=1&csb=default&cs=ASC&pball=), [R01 ES021369-05](https://projectreporter.nih.gov/project_info_description.cfm?aid=9210551&icde=37849782&ddparam=&ddvalue=&ddsub=&cr=1&csb=default&cs=ASC&pball=), and [P42 ES004705-29](https://projectreporter.nih.gov/project_info_details.cfm?aid=9260357&map=y).

@@

&copy; 2017-2018 [Nima S. Hejazi](https://nimahejazi.org)
